Smart Spreading Factor Assignment for LoRaWANs

### 2019-05-01 paper.tex
ack grammer

\subsection{Smart SF Schemes}
PDR and transmit energy consumption plots of the lowest SF, random SF and the smart prediction schemes are shown in Figure \ref{fig:prediction_pdr} and \ref{fig:prediction_energy}. Randomly generated network radius is set to 5000 meters and number of gateways is set to 3. Prediction model needs nodes' locations and three gateways are enough to locate position of nodes by triangulation. In Table \ref{table:prediction_pdr}, PDR values for various network radii are presented. Random SF scheme consumes far more energy than others, therefore it is not feasible for real world deployments. As number of nodes increases, both smart SVM and smart DTC schemes consume slightly more energy than lowest SF scheme, however they give better PDR results in return. Increasing number of nodes, increases number of interferences. Smart schemes improve network performance when LoRa interference is high. Moreover, smart schemes give better PDR results when nodes are deployed closer to the gateway, since nodes have margin to increase their SFs when they are deployed closer to the gateway. If a node is far away from gateway, then smart schemes cannot increase the SF to avoid interference since the assigned SF is already high.

@@

\section*{Acknowledgment}
This work is supported by Turkish Ministry of Development and Istanbul Technical University researcher support program under the Grant No. ITU-AYP-2017-1.

>>>>

\subsection{Smart SF Schemes}
PDR and transmit energy consumption plots of the lowest SF, random SF and the smart prediction schemes are shown in Figure \ref{fig:prediction_pdr} and Figure \ref{fig:prediction_energy}. Randomly generated network radius is set to 5000 meters and number of gateways is set to 3. Prediction model needs nodes' locations and three gateways are enough to locate position of nodes by triangulation. In Table \ref{table:prediction_pdr}, PDR values for various network radii are presented. Random SF scheme consumes far more energy than others, therefore it is not feasible for real world deployments. As number of nodes increases, both smart SVM and smart DTC schemes consume slightly more energy than lowest SF scheme, however they give better PDR results in return. Increasing number of nodes, increases number of interferences. Smart schemes improve network performance when LoRa interference is high. Moreover, smart schemes give better PDR results when nodes are deployed closer to the gateway, since nodes have margin to increase their SFs when they are deployed closer to the gateway. If a node is far away from gateway, then smart schemes cannot increase the SF to avoid interference since the assigned SF is already high.

@@

\section*{Acknowledgment}
This work is supported by the Turkish Ministry of Development and Istanbul Technical University researcher support program under the Grant No. ITU-AYP-2017-1.
